A Sample Article Using `quarto-ieee` for IEEE Journal and Transactions

### 2025-01-02 Code/R/RMarkdown/Report_goodness-of-fit.Rmd
new codes

load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
#load("../Programs/Data/results_ottawa_city_512_7_AO_300b.Rdata")#results_ottawa_city_512_7_AO_300b.Rdata
#load("../Programs/Data/results_Chicago_1024_9_AO_100b_6L.Rdata")
#results_Chicago_1024_9_AO_100b_6L
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_AO_100b.Rdata")
#save(p_values_matrix, epsilon_matrix, file = "./Data/results_pvalue_epsilon.Rdata")
load("../Programs/Data/results_Chicago_1024_9_AO_200b_36L.Rdata")
#x1<-as.vector(epsilon_matrix)
source("../imagematrix.R")
hist(difference_values)

>>>>

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
#load("../Programs/Data/results_ottawa_city_512_7_AO_300b.Rdata")#results_ottawa_city_512_7_AO_300b.Rdata
#load("../Programs/Data/results_Chicago_1024_9_AO_100b_6L.Rdata")
#results_Chicago_1024_9_AO_100b_6L
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_AO_100b.Rdata")
#save(p_values_matrix, epsilon_matrix, file = "./Data/results_pvalue_epsilon.Rdata")
#load("../Programs/Data/results_Chicago_1024_9_AO_200b_36L.Rdata")
#save(p_values_matrix, z_scores_matrix, file = "./Data/results_pvalue_Flevoland_300_7_v6.Rdata")
load("../Programs/Data/results_Phantom_4_renyi_B200_w9_08_L5.Rdata")
#x1<-as.vector(epsilon_matrix)
source("../imagematrix.R")
hist(difference_values)

### 2025-01-02 Text/Articles/quarto-ieee-example/ieee-template.qmd
new codes

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)

@@

@@

```{r}
#| label: fig-density0
#| fig-cap: Simulated data from a N(0,1) distribution.
#| fig-pos: "H"
set.seed(2022-12-20)
df <- tibble(x = rnorm(200))
df |>
  ggplot(aes(x=x)) +
  geom_density(bw = "sj") +
  geom_rug()
```

>>>>

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)#, eval = FALSE

@@

```{r}
#| eval: false
#| echo: false
# This chunk will neither execute nor display the code
set.seed(123)
data <- rnorm(1000)
plot(density(data), main = "Density plot of 1000 random normal numbers")

@@

```{r}
#| label: fig-density0
#| fig-cap: Simulated data from a N(0,1) distribution.
#| fig-pos: "H"
#| eval: true
set.seed(2022-12-20)
df <- tibble(x = rnorm(200))
df |>
  ggplot(aes(x=x)) +
  geom_density(bw = "sj") +
  geom_rug()
```
